Articular cartilage corefucosylation regulates tissue resilience in osteoarthritis

Version 1

Abstract

Abstract

This study aimed to investigate the glycan structural changes that occur before histological degeneration in osteoarthritis (OA) and to determine the mechanism by which these glycan conformational changes affect cartilage degeneration. An OA model was established in rabbits using mannosidase injection, which reduced high-mannose type N-glycans and led to cartilage degeneration. Further analysis of glycome in human OA cartilage identified specific corefucosylated N-glycan expression patterns. Inhibition of N-glycan corefucosylation resulted in unrecoverable cartilage degeneration, while cartilage-specific blocking of corefucosylation led to accelerated development of aging-associated and instability-induced OA models. We conclude that α1,6 fucosyltransferase is required postnatally to prevent preosteoarthritic deterioration of articular cartilage. These findings provide a novel definition of early OA and identify glyco-phenotypes of OA cartilage, which may distinguish individuals at higher risk of progression.

Introduction

Osteoarthritis (OA), a degeneration of joint components, such as proteoglycans (PGs) and collagen, destroys cartilage and impairs joint function (1). The global prevalence of OA is estimated to be >500 million, which is a significant socioeconomic burden (2). Therefore, preventive measures must be implemented to reduce the future disease burden and disability. Once the cartilage is destroyed, it cannot be repaired homogeneously and progresses irreversibly thereafter (3, 4). Since articular cartilage has no blood vessels and is not innervated, it is difficult for symptoms to appear. By the time clinical symptoms appear, the condition is often already considerably advanced (5). Therefore, from a preventive perspective, it is necessary to define and detect “pre-OA,” the stage before the onset of early OA (6, 7). Pre-OA is a knee with no pain, no motor function problems, and no arthroscopic or structural changes on radiography, only emerging cellular effects. Despite many studies, there is no gold standard for OA biomarkers (8). It is important to characterize the disease state before OA to shift the paradigm from mitigation to late-onset disease prevention.

In the very early stages of OA, before cartilage matrix degeneration, cartilage destruction by enzymatic processes that degrade glycoproteins, PGs, and collagen, in that order, is underway (9). Collagenolytic activity is largely unchanged on intact articular surfaces (10, 11), and glycoprotein degradation is thought to be an early transient event in the enzymatic process of cartilage destruction because hexose degradation of glycoproteins promotes degradation of the protein portion of the molecule by proteinases (12). Additionally, cartilage damage is reversible if type 2 collagen breakdown is mild (13). Structural change analysis in glycoproteins is necessary for the early stages of OA but has not yet been performed sufficiently.

Matsuhashi et al.’s study showed that structural changes in N-glycans occurred in degenerated cartilage in a rabbit OA model before tissue changes occurred (14). Urita et al. demonstrated that these N-glycans in degenerated mice and human cartilage are high-mannose type N-glycans (15). Furthermore, among several glycosidases, mannosidase activity was very high in OA joints, and its activity was high before the progression of cartilage fibrosis (16). This suggests that high-mannose type N-glycan plays an important role in OA pathogenesis. However, whether changes in the glycan structure are involved in OA pathogenesis is unclear.

This study analyzed the glycan structural changes that preceded OA degeneration and elucidated the mechanism of glycan structural changes in cartilage degeneration. For this purpose, the effects of mannosidase, a specific degrading enzyme of high-mannose type N-glycans associated with OA, on cartilage tissues and its molecular mechanisms were analyzed.

Results

Mannosidase injection caused early OA-like change in vivo

A decrease in Safranin O staining in the right femoral condyle of the α-mannosidase-injected knee after 4 weeks was observed (Fig. 1A, B). Terminal deoxynucleotidyl transferase dUTP nick end labeling (TUNEL) staining was enhanced in the superficial layer compared with that in control. Articular cartilage chondrocytes exposed to α-mannosidase were not arranged in columns in the middle zone. The surfaces of each group were smooth and had a good macroscopic appearance (Fig. 1C). None of the groups showed a decrease in type 2 collagen staining, and the orientation was maintained (Fig. 1D). To achieve optimal activity, the pH range of 4 to 5 is ideal for mannosidase. In a physiological saline solution with a pH of 7 and a concentration of 100 μg/ml, it exhibited specific activity. Nevertheless, at a concentration of 1.0 μg/ml, this activity was no longer present (S1 Figure). The mean histological score of the α-mannosidase group was 0.83, indicating mild OA (Fig. 1E). The control group was unchanged. Cartilage degeneration during intermittent intra-articular administration of mannosidase was reversed upon discontinuation (Fig. 1F).

Effects of α-mannosidase injection in the knee joint in vivo.

(A) Time course of intra-articular α-mannosidase injection and unloading. Red arrows indicate the one-shot, intra-articular injection that was performed once a week. (B) Histological evaluation of knee articular cartilage 4 weeks after intermittent α-mannosidase infusion and 16 weeks after load removal. Scale bars, 50 μm. (C) Representative macroscopic assessment of the articular cartilage using mannosidase concentration. Scale bar, 1 cm. (D) Evaluation of the collagen orientation of reparative tissues at 4 weeks postoperatively. Sections stained with HE was viewed under a polarized light microscope at multiple angles (0°, 45°, and 90°). Scale bar, 200 μm. (E) OARSI scores at 4 weeks postoperatively on sections from the knee joint (n = 6). (F) Tissue degeneration scores at each time point are based on mannosidase concentration. Data are shown as mean ± standard deviation. *P < 0.05, **P < 0.01 versus the saline group in (E), and versus 4 weeks in (F). In (E), the Welch t-test was used for statistical analysis. In (F), n = 6 rabbits per group. One-way analysis of variance with Tukey’s multiple comparison test was used to perform statistical analysis. HE, hematoxylin and eosin; OARSI, Osteoarthritis Research Society International; TUNEL, terminal deoxynucleotidyl transferase dUTP nick end labeling.

Depletion of high-mannose type N-glycans in chondrocytes leads to cartilage degradation ex vivo

To quantify the degeneration and resilience promoted by the injection of α-mannosidase, the cultured cartilage was harvested at different time points (Fig. 2A). Concanavalin A (Con A) reactivity declined in articular cartilage treated with α-mannosidase (Fig. 2B). The application of α-mannosidase stimulated the release of PG from cultured cartilage in association with extracellular matrix degradation (Fig. 2C) and showed significantly higher spontaneous nitric oxide (NO) release than the control over time (Fig. 2F). Mannosidase-exposed cartilage showed an increase in TUNEL-positive cells in chondrocytes in the deep zone and type 10 collagen-positive cells in superficial chondrocytes; however, these changes did not occur in cytokine-stimulated cartilage (S2 Figure). Mannosidase exposure increased Adamts5 expression and suppressed Mmp13 expression and anabolic factors (Fig. 3E). In the articular cartilage that was exposed to freeze-thaw treatment before culture, no differences in PG loss were observed between the α-mannosidase-stimulated cartilage and non-stimulated cartilage (Fig. 2E). Excluding mannosidase loading, PG leakage and Safranin O staining were restored (Fig. 2D), but Con A staining loss was not. Sialidase addition did not cause PG leakage or NO production (S3 Figure), and the aggrecan lost in the catabolic phase was not replenished in the subsequent anabolic phase.

Cartilage degradation induced by mannosidase stimulation.

(A) Schematic diagram of the procedures used to establish the early OA model before irreversible and progressive destruction of articular cartilage. (B) Mannosidase-treated cartilage stained with Safranin O and Con A. The distribution of high-mannose type N-glycans is decreased in mannosidase-induced degraded mouse cartilage. Scale bars, 50 μm. (C), (D) PG release after exposure to mannosidase (C) and recovery after its removal from cultured cartilage grafts (D). (E) To investigate the non-chondrocyte-mediated release of fragments, PG loss was measured in cartilage explants that had undergone freeze-thaw cycles. (F) Sequential NO released into media measured as concentrations of nitrite for cartilage explants stimulated with mannosidase. Data are shown as mean ± standard deviation (s.d.). *P < 0.05, **P < 0.01 versus the control group in c, e, and (F), and versus day 3 in (D). In (C) and (E), n = 3 samples (six mice) per group. One-way ANOVA with the Tukey multiple comparison test was used to perform statistical analysis. In (D), n = 12 mice in each group and n = 3 samples (six mice) at each time point. In (F), n = 16 mice at each time point and n = 4 samples (eight mice) per group. In (D) and (F), two-way ANOVA with the Sidak multiple-comparisons test was used to perform statistical analysis. Con A, concanavalin A; NO, nitric oxide; ANOVA, analysis of variance; PG, proteoglycan.

Cartilage N-glycomes.

(A) MALDI-TOF MS spectra showing the quantitative N-glycan profiles of cartilage before (upper) and after (lower) mannosidase treatment. (B) Scatter plot of the changes in m/z per protein abundance in the mannosidase (x-axis) and control (y-axis) N-glycan structures. The red dots indicate the top 10 N-glycan structures based on the deviation from the y = x line. (C) Heatmap of N-glycome showing differential N-glycan expression in the mannosidase (man+) group versus the control (man-) group. (D) N-glycans altered by mannosidase were corefucosylated glycans and high-mannose type N-glycans. (E) RT-PCR expression analysis of marker genes in organ culture of cartilage with mannosidase. Data are shown as mean ± standard deviation. *P < 0.05, **P < 0.01 versus the control group in (D), and versus 0 hours in (E). In (D) and (E), n = 3 samples (six mice) per group. In (D), unpaired t-tests were used to perform statistical analyses. In (E), one-way ANOVA with the Dunnett multiple comparison test was used to perform statistical analysis. MALDI-TOF MS, matrix-assisted laser desorption/ionization-time of flight mass spectrometry; ANOVA, analysis of variance; RT-PCR, real-time polymerase chain reaction.

Corefucosylated N-glycan was formed in resilient cartilage

Glycoblotting analysis revealed a significant difference in the N-glycan profiles (Fig. 3A and S1 Table). Plotting m/z after mannosidase exposure against m/z before mannosidase exposure demonstrated that only N-glycans were affected by enzyme dissociation from the y = x line (Fig. 3B, S2 Table). In both denatured and reverted cartilages, Man8-9GlcNAc2 was decreased, and Man5-6GlcNAc2 was increased by the action of mannosidase, which has a high specificity for the terminal mannosidic residues of glycans (Fig. 3C, D). In contrast, corefucosylated N-glycans, which were formed in the same biosynthesis pathway, were also found (Fig. 3D). Similarly, the N-glycan profiles of isolated chondrocytes showed the presence of this corefucosylated structure (S4 Figure). The expression of Fut8, the only enzyme involved in corefucosylation, increased significantly in mannosidase-treated cartilage (Fig. 3E).

Deficiency of corefucosylated glycans in articular cartilage inhibits recovery from cartilage damage and promotes cartilage degeneration

We first examined whether the absence of core fucose affects the resilience of cartilage degeneration. Mice lacking Fut8 exhibited severe growth retardation and died shortly after birth. Therefore, we decided to generate Fut8 conditional knockout (cKO) mice (Fig. 4A, B). The tissue specificity of recombination was confirmed by polymerase chain reaction (PCR) analysis of mouse genomic DNA that detected either the intact Fut8loxP allele or the Cre-recombined Fut8Δ allele in repeated crosses; N-glycan analysis of cartilage demonstrated the loss of corefucosylated sugar chains (Fig. 4C). The proportion of high-mannose type N-glycan content was unchanged in cartilage lacking the Fut8 gene (S5 Figure). Next, we used real-time (RT)-PCR to determine relative Fut8 messenger (m)-RNA levels in the cartilage of Col2-Fut8−/− mice and their wild-type (WT) littermates (Fut8loxP/loxP). Real-time polymerase chain reaction (RT-PCR) analysis showed that Fut8 mRNA expression was reduced by >99% in the articular cartilage of Col2-Fut8−/− mice compared to that in their WT littermates (P < 0.01; n = 3 mice per group) (Fig. 4D). Chondrocyte-surface corefucosylation levels were analyzed by lectin staining using Pholiota squarrosa lectin (PhoSL), which specifically recognizes α1-6 core fucose (17). PhoSL lectin staining was completely absent in the articular cartilage of Fut8 cKO mice, in contrast to the positive staining observed in Fut8 flox mice under physiological conditions (Fig. 4E). Enzymatic degradation of high-mannose type N-glycans on the cartilage in Fut8-deficient mice exacerbated cartilage degeneration (Fig. 4E, F). In addition, reversible matrix repair by enzyme removal observed in control cartilage was not observed in Fut8-deficient cartilage explant cultures.

Loss of resilience due to FUT8 deficiency in cartilage.

(A) Biological reaction of FUT8. FUT8 transfers fucose to the innermost GlcNAc residue of complex N-glycans via α1,6-linkage (corefucosylation). (B) Targeted disruption of Fut8 locus. The Fut8 gene (WT allele; top), targeting vector (middle), and disrupted Fut8 locus (mutant allele; bottom). Schematic representation of the Fut8-targeting strategy and Cre-mediated recombination of the Fut8loxP allele. (C) MALDI-TOF MS mass spectra of N-glycans from WT and Fut8 cKO mice. The corefucosylation levels in cartilage were decreased and undetectable in Fut8 cKO mice. (D) Gene profile in chondrocytes isolated from Fut8 cKO mice. The expression levels of these genes in WT cells were set to 1. PPIA, peptidylprolyl isomerase A. (E) Histological findings in cartilage explants from Fut8 cKO mice and their floxed littermates, cultured with mannosidase and subjected to Safranin O staining and PhoSL lectin staining. Scale bar, 50 μm. (F) PG release in cultured cartilage explants from Fut8 cKO mice and their floxed littermates. Data are shown as mean ± standard deviation. In (E), n = 3 samples (six mice) per group. *P < 0.05, **P < 0.01 versus the control group. One-way ANOVA, with the Tukey multiple comparison test, was used to perform statistical analysis. MALDI-TOF MS, matrix-assisted laser desorption/ionization-time of flight mass spectrometry; WT, wild-type; cKO, conditional knockout; PG, proteoglycan; ANOVA, analysis of variance.

Loss of corefucosylated glycans in articular cartilage leads to premature OA

Col2-Fut8−/− mice developed and grew normally without major organ abnormalities of major organs and could not be distinguished from their WT littermates. The whole skeletons of newborn mice stained with alcian blue and alizarin red did not differ in appearance between the genotypes (Fig. 5A). Col2-Fut8−/− mice showed a lower body weight than their WT littermates, as indicated by the growth curve (Fig. 5B). We analyzed the development of instability-induced OA changes in Fut8loxP/loxP and Fut8 cKO mice. Sham operations produced no significant changes in OA in either mouse genotype. Eight weeks after instability-inducing surgery, the joints of WT mice developed changes in OA, such as cartilage erosion and a reduction in Safranin O staining and chondrocyte number. Deletion of FUT8 results in more severe changes in OA. In the joints of Fut8 cKO mice, 8 weeks after surgery, the noncalcified zone (upper layer above the tidemark) was almost completely lost. The number of chondrocytes was significantly reduced (Fig. 5C). Quantitative assessment using the OA Research Society International (OARSI) score supported these histological findings (difference: -2.900; Fut8flox/flox/destabilization of the medial meniscus (DMM) versus Col2a1-Cre; Fut8flox/flox/DMM, 95% confidence interval [CI] for the difference: -5.027 to - 0.7734) (Fig. 5D). Changes in OA progressed earlier in the aging models of Fut8-deficient mice than in control mice (WT and floxed mice). The mice were followed up until 15 months of age to assess the spontaneous development of OA with aging (Fig. 5E). There were no apparent changes of OA in the knee joints of either mouse genotype at 3 months of age (Fig. 5F). At 4 months of age, significant changes in OA were detected in the knee joints of the Fut8 cKO mice. The cartilage surface integrity was no longer maintained at 9 months. These OA changes progressed more in Fut8 cKO mice than in their WT littermates at 15 months. These histological findings were quantitatively confirmed by the Osteoarthritis Research Society International (OARSI) scores (difference: -2.000; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -3.723 to -0.2771 at 4 months, difference: -2.700; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -4.423 to -0.9771 at 9 months, and difference: -6.700; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -8.423 to - 4.977 at 15 months).

OA acceleration in Fut8 cKO mice.

(A) Double staining with alizarin red and alcian blue of the whole skeleton of wild-type and Col2a1-Cre;Fut8flox/flox cKO littermate embryos (newborn). Scale bars, 1 cm (left). Weight and body length of wild-type and cKO littermate embryos (right). (B) Growth curves determined by body weight in male (left) and female (right) wild-type mice and their cKO littermates. (C), (D) Features of instability-induced OA in Fut8flox/flox (flox) mice and their cKO littermates at 8 weeks after surgery. Safranin O staining is shown for each mouse genotype. Scale bar, 100 μm (C). Summed histological scores for OA severity in the knee cartilage from flox and cKO mice, as determined using the OARSI scoring system, are shown (D). (E), (F) Features of age-associated osteoarthritis in wild-type mice and their flox and cKO littermates. Safranin O staining of the knee joint is shown for each mouse genotype at 3, 4, 9, and 15 months of age. Scale bar, 100 μm (E). The summed OARSI scores are shown (F). Data are shown as mean ± standard deviation. In (A), the Welch t-test was used to perform statistical analyses (n = 6 mice per group). In (B), n = 15 mice per group at each time point. In (D) and (F), n = 5 mice per group at each time point. *P < 0.05, **P < 0.01 versus the wild-type group in (B) and (F), and versus flox mice in (D). One-way ANOVA with the Tukey multiple comparisons test (B), (D) and two-way ANOVA with the Tukey multiple comparisons test (F) were used to perform statistical analysis. OA, osteoarthritis; cKO, conditional knockout; OARSI, Osteoarthritis Research Society International. ANOVA, analysis of variance; ns, not significant.

Altered glycosylation of human OA cartilage based on comprehensive glycan analysis

Total glycome profiling of human OA cartilage is shown in Fig. 6A and S3 Table. The amount of high-mannose type N-glycan was significantly decreased, the same as previously reported in OA cartilages (Fig. 6A) (15). Focusing on fucosylation, most of the complex/hybrid type glycans were modified with fucose. The fucosylation that occurs at the innermost N-acetylglucosamine (GlcNAc) of N-glycans could be recognized with a lectin from the mushroom Pholiota squarrosa (PhoSL) and was able to detect the expression of the corefucose structure. Therefore, we suspected that the stainability of PhoSL is increased in OA cartilage. As expected, the PhoSL staining of OA cartilage was significantly increased relative to that of a healthy control (Fig. 6B). We performed principal component analysis (PCA) on 1110 glycomic data, discriminating OA from healthy cartilages along the first principal component (PC1) axis (Fig. 6C). Hierarchical cluster analysis showed that clades containing corefucosylated glycans were clustered (Fig. 6D), and N-13 ((Hex)1 (HexNAc)1 (Fuc)1 + (Man)3(GlcNAc)2) has the largest squared correlation with its cluster component.

Altered glycosylation of human Osteoarthritis (OA) cartilage based on comprehensive glycan analysis.

(A) Total glycome profiling of human OA cartilage. Pie charts at the vertices of the pentagon correspond to the glycan expression profiles of N-glycans, O-glycans, GSL-glycans, free oligosaccharides (fOS), and glycosaminoglycan (GAG). The size of each circle and its constituent colors reflect the absolute quantity of glycans (pmol/100 μg protein) and the glycan substructures, respectively. The sizes of the circles representing the GAG contents are increased by 10-fold. Each color indicates the estimated glycan structure and corresponds to the respective glycan number listed in the S3 Table. (B) Expression of core fucose in healthy and OA cartilage. Scale bar, 100 μm. (C) Principal component analysis (PCA) of a glycan expression data set. Data points represent individual samples. The first principal component (PC1) distinguishes healthy and OA samples. (D) Hierarchical cluster analysis results showing cluster image display for total glycans with color gradient for relative glycan expression and dendrogram for each glycan structure. Cluster summary of PCA on the glycome are shown on the right. The most representative variable is (Hex)1 (HexNAc)1 (Fuc)1 + (Man)3(GlcNAc)2 that means the largest squared correlation with its cluster component.

Discussion

To test the hypothesis that structural changes in high-mannose type N-glycans may induce OA, we tested the effect of mannosidase loading on the structure of high-mannose type N-glycans. Consequently, modifying the structure of high-mannose type N-glycans by mannosidase loading induced OA-like histological alterations. Furthermore, the OA-like changes induced by mannosidase were recovered by enzyme removal. These results suggest that structural alterations of high-mannose type N-glycans lead to OA-like histological changes in articular cartilage but do not necessarily cause the pathogenesis of eventual OA. Subsequently, glycoblotting analysis revealed that core-fucose-containing glycans underwent complementary structural alterations per high-mannose type N-glycans. This suggests that the structural change of core-fucose-containing glycans may have some compensatory mechanism for OA-like alterations caused by the structural change of high-mannose type N-glycans. Furthermore, under the regulation of Fut8 expression, which regulates the synthesis of core fucose, mannosidase was found to induce irreversible OA. These results provide the first evidence that structural alterations in glycans in the articular cartilage regulate eventual OA development.

Two key targets of cartilage degeneration during OA are type II collagen, a major substrate of matrix metalloproteinase (MMP)-13 (18), and aggrecan, a PG with glycosaminoglycan side chains of chondroitin and keratin sulfate (19, 20). The degradation of non-collagenous molecules, such as aggrecan, occurs before the degradation of type II collagen in the early stages of OA (20, 21). The histological analysis in this study revealed that the alteration in the structure of high-mannose type N-glycans resulted in a decrease in Safranin O staining (a decrease in glycosaminoglycans and/or PGs), whereas there was no change in collagen staining. These findings are consistent with alterations in the early stages of OA. Furthermore, we observed that removing mannosidase could cause PG loss to the control level. Karsdal et al. demonstrated that articular cartilage degradation is reversible in the presence of aggrecanase and concluded that the repair ability is not impaired before the degradation of aggrecan and type II collagen by MMPs (22). Reimann et al. observed that the glycosaminoglycans loss in articular cartilage is reversible and an early sign of OA before the “state of no return.” (23) The present results are consistent with findings of previous reports on early OA and suggest that the mannosidase-loaded model can be considered an early OA-like alteration.

Since the structural change in high-mannose type N-glycans alone did not cause irreversible OA, we investigated other regulatory mechanisms related to high-mannose type N-glycans that could induce irreversible OA. The expression of corefucosylated N-glycans on a series of biosynthetic pathways was upregulated with structural changes in high-mannose type N-glycans. FUT8 is known to corefucosylate small oligomannose N-glycans (Man4-Man5GlcNAc2) but not large oligomannose N-glycans, such as Man8-Man9GlcNAc2 (24). This suggests that small oligomannose N-glycans trimmed by mannosidase could activate Fut8. Fut8 is also upregulated in human OA chondrocytes (25, 26), and increased expression of these corefucosylated N-glycans has been observed during late chondrocyte differentiation (27). These findings suggested that these structural changes are related to OA-related glycosylation.

To clarify the relationship between the alteration of corefucosylated N-glycans and cartilage degeneration, Fut8 cKO mice were used. Since the results of the ex vivo freeze-thaw model showed that cartilage degeneration was induced by changes in the glycan structure of chondrocytes, we used chondrocyte-specific KO mice. As a result, the reversibility of the cartilage degeneration model was diminished. This finding suggests that Fut8-mediated corefucosylation in chondrocytes plays a function in promoting glycan repair. Furthermore, to directly determine whether Fut8 was involved in the inhibition of OA progression, an aging model was investigated. The results showed that conditional KO of Fut8 in chondrocytes hastened the onset of OA. This suggests that cartilage corefucosylation associated with FUT8 plays a protective role against the attenuation of type II collagen in the OA process. Finally, the expression of α1,6-linked core fucose on N-glycans in human cartilage is associated with OA, and corefucosylation was found to be one of the characteristics in OA cartilage. Total cellular glycome analysis, including N- and O-linked glycans derived from glycoproteins, GSL-glycans, GAGs, and fOSs, is informative for analyzing cell-specific characteristics (28‒30). Glycome profiling enabled the detection of corefucosylated N-glycans by sequential clustering of degenerated cartilage characteristics. Core fucose deficient mice generated by ablating the α1,6 fucosyltransferase enzyme, FUT8, were reported to have suppressed phosphorylation of Smad and increased expression of MMPs (matrix metalloproteinases) due to decreased binding of TGF-β ligand caused by the lack of core fucose addition to the TGF-β type II receptor (31, 32). The present study shows that treatment of cartilage with mannosidase caused corefucosylation, suppression of Mmp13, and increased expression of Tgf-β. Moreover, treatment of FUT8-knockout cartilage with mannosidase resulted in the suppression of Tgf-β expression and increased Mmp13 expression. These results suggest that corefucosylation following the loss of high-mannose type N-glycans may provide chondroprotective effects via the TGF-β signaling pathway, which may have been lost by FUT8-knockout.

One limitation of this study was that we did not have access to cartilage samples from immediately before the onset of OA; thus, we do not know the expression of Fut8 in human cartilage in the early stage of OA onset and its influence on extracellular matrix degradation under homeostatic conditions. Obtaining cartilage specimens continues to be challenging, especially for those with early stages of OA.

In summary, we show for the first time a key role of FUT8 and glycan-dependent signaling mediators in extracellular matrix resilience associated with cartilage corefucosylation during early OA.

Methods

Intra-articular injection of α-mannosidase in the knee

Japanese White rabbits weighing 3.10 ± 0.15 kg purchased from a professional breeder (Japan SLC Inc., Hamamatsu, Japan) were used for this study according to established ethical guidelines approved by the local animal care committee. Animals were anesthetized with 10 mg/kg of intravenous ketamine, followed by isoflurane in oxygen gas. Both knees in each rabbit were shaved, prepared, and draped in a sterile fashion. α-Mannosidase from Canavalia ensiformis (Jack bean) (Sigma, St Louis, MO, USA) was dissolved in saline. Five hundred microliter volumes containing 1.9 units per ml (0.05 mg) of mannosidase solution were injected into the joint cavity of the right knee. α-Mannosidase from Canavalia ensiformis (Jack bean) has been widely used as a tool for glycan analysis, which has a high specificity towards terminal mannosidic residues of glycans and participates in mannose trimming reactions (33). The measurement of its performance in a saline solution was evaluated using the QuantiChrom α-Mannosidase Assay Kit (BioAssay Systems, Hayward, CA, USA). This colorimetric assay uses 4-nitrophenyl-α-d-mannopyranoside as a substrate to identify the generation of 4-nitrophenol. The following doses of α-Mannosidase were administered: 0.5 ml at 0.01 μg/ml, 1.0 μg/ml, or 100 μg/ml. Simultaneously, the contralateral knee joint received an equal volume of saline solution. Each joint was injected once or four times in alternate weeks. The animals were euthanized at 4 and 16 weeks postoperatively. Each section of the knee joint was stained with hematoxylin and eosin or Safranin O/fast green, as well as with immunohistochemical staining for type II collagen and TUNEL. Two investigators quantified the OA severity using the OARSI scoring method.

Evaluation of collagen orientation by a polarized light microscope

To evaluate the collagen orientation of the repaired tissue at 16 weeks postoperatively, a supplemental evaluation using a polarized light microscope (PLM) (ECLIPSE E600 POL; Nikon, Tokyo, Japan) was conducted (34). This evaluation was performed on HE-stained sections from each group. Two cross polarizers were used so that highly ordered collagen perpendicular to the articular surface appeared bright, while collagen that was not ordered (nonbirefringent) appeared dark. The contrast of fibrils more parallel to the articular surface was darker than collagen oriented perpendicular to the articular surface. To observe the predominant direction of the birefringent regions and confirm the lack of orientation in the nonbirefringent regions, the sections were rotated at 0°, 45°, and 90° for the fixed filters. Microscopic images were acquired using a digital camera (DS-5M-L1, Nikon, Tokyo, Japan). Each sample was examined independently by an experienced PLM user.

Ex vivo analysis of deletion of high-mannose type N-glycan in cartilage

According to the established ethical guidelines approved by the local animal care committee, cartilage catabolism was analyzed by culturing femoral head cartilage of 4-week-old C57BL6 male mice with α-mannosidase (1.9 U/mL) ex vivo (35, 36). Mannosidase was removed on day 3, and organ culture was continued until day 6. To evaluate cartilage degradation, quantification of PG release from cartilage explants was performed using the dimethylmethylene blue assay (36, 37) and exposure to sialidase (1.9 U/mL) and interleukin-1 beta (Cat #. 300-01A; BioLegend, San Diego, CA, USA) (10 ng/mL) was also used as another control. The NO concentration in the culture medium was measured using the Griess reagent system (Promega, Tokyo, Japan). To determine the direct effects of mannosidase on the matrix, some cartilage explants were subjected to freeze-thaw cycles in liquid nitrogen to destroy chondrocytes present in the superficial layer of the cartilage (22, 38). After the procedure, the cells were replaced with the same culture medium described above. Each tissue sample was stained with Safranin O. Lectin staining with Con A (Wako Pure Chemical Industries, Richmond, VA, USA) and PhoSL (J-Oil Mills Inc., Tokyo, Japan) was used to detect the high-mannose type N-glycans. Staining was performed using the ABC Kit (Vector Labs, Burlingame, CA, USA), and the sections were counterstained with HE.

RNA extraction and quantitative RT-PCR analysis

Total RNA was extracted from the samples using an RNeasy Mini Kit (Qiagen, Hilden, Germany). For complementary DNA synthesis, 1.0 μg of RNA was reverse transcribed using random hexamer primers (Promega, Tokyo, Japan) and ImProm II reverse transcriptase (Promega). Quantitative RT-PCR was performed using a Thermal Cycler Dice Real Time System II (Takara Bio Inc., Otsu, Japan) and SYBR Premix Ex Taq II (Takara, Shiga, Japan) with gene-specific primers (S4 Table) in 15 μl of the mixture, following the manufacturer’s instructions. Quantitative data were normalized using peptidylprolyl isomerase A as an endogenous reference gene and were calculated using the ΔΔCt method (39).

Generation of Fut8loxp/loxpCol2a1-Cre cKO mice

Fut8loxp/loxp mice were provided by Tohoku Pharmaceutical University (Sendai, Japan). To interrupt the synthesis of corefucosylated N-glycans in cartilage, we generated mice with knockout of the chondrocyte-specific Fut8 gene (Col2-Fut8-/- mice) by crossing Fut8loxp/loxmice with Col2a1-Cre–transgenic mice (40), in which Cre recombinase is expressed specifically in chondrocytes under the Col2a1 promoter. Transgenic mice carrying the Col2a1-Cre transgene (strain B6; SJL-Tg [Col2a1-Cre] 1Bhr/J; stock number 003554) were obtained from the Jackson Laboratory (Bar Harbor, ME, USA). Homozygous Fut8loxp/loxpmice were bred with Col2a1-Cre mice, and offspring with the genotype Fut8loxp/+ Col2a1-Cre were bred with Fut8loxp/loxp mice to obtain the Fut8loxp/loxpCol2a1-Cre cKO experimental group and Fut8loxp/loxp (flox) littermate controls. All animals were maintained at Hokkaido University under the regulations of the Institutional Animal Care and Use Committee.

Skeletal examination

To observe the skeletal systems, whole skeletons of WT and cKO littermates were stained with alcian blue and alizarin red, as previously described (41, 42). The newborns were skinned, eviscerated, and fixed in 95% ethanol. Intact skeletons were stained with 150 mg/ml of alcian blue 8GX in 75% (vol/vol) ethanol/20% acetic acid for 24–48 hours, and excess tissues were removed by 1–2% KOH digestion for 2–3 days. The skeletal preparations were stained with 75 mg/ml of alizarin red S in 1% KOH for 24 hours and cleared in graded glycerol solutions (43).

Instability-induced OA model

An OA model was created in 10-week-old mice by destabilizing the knee joint as previously described (44). With the mice under general anesthesia, we destabilized the right knee joint by transection of the medial collateral ligament and removing the cranial half of the medial meniscus using a microsurgical technique (DMM). A sham operation was performed on the left knee joint using the same approach, without ligament transection and meniscectomy. For histological assessment, the mice were sacrificed, and the entire knee joint was dissected 8 weeks postoperatively.

Age-associated OA model

At 3, 4, 9, and 15 months of age, the mice were sacrificed, and their entire knee joints were dissected to assess the spontaneous development of OA as a model of age-associated OA (44, 45).

Human Cartilage Preparation

Acquisition and use of patient tissues were approved by the institutional review board (IRB) of Hokkaido University (approval number: 014-0144), and informed consent was obtained in advance. Samples were from patients undergoing total knee arthroplasty for clinically and radiologically diagnosed OA (n=5; age range 61–84 years, mean 72.4; male: female ratio 1:4). Age-matched control articular cartilage was from patients undergoing total hip arthroplasty for femoral neck fracture with no history of joint disease (n=5; age range 45–88 years, mean 61.2 years; male: female ratio 3:2). Each cartilage specimen was evaluated macroscopically by at least two veteran doctors to ensure that it had not suffered damage or degeneration and was treated within 9 hours of harvest in the operating room. Immediately upon receipt, isolated human cartilage was homogenized with a Polytron blender (Kinematica, Luzern, Switzerland), and then cold ethanol was added to separate the protein and lipid fractions.

Total cartilage glycomic analysis

N-glycans were released directly using cartilage lysates following deglycosylation by overnight treatment with peptide N-glycanase F (PNGase F, 2U) (Roche, Switzerland). The supernatants containing GSLs and fOSs were dried with a centrifugal evaporator. GSL-glycans were isolated by enzymatic digestion using EGCase I (Takara Bio Inc. Japan), whereas fOSs were recovered from an EGCase I-free fraction (46). Cartilage lysate was delipidated and digested by GAG disaccharides (47). Extracted glycoproteins were subjected to BEP for O-glycan analysis. Detailed procedures and materials are provided elsewhere (48). N-glycans, fOSs, GAGs, and GSL-glycans were subjected to glycoblotting (49). Purified N-glycans, fOSs, O-glycans, and GSL-glycan solutions were mixed with 2,5-dihydrobenzoic acid and subjected to Matrix-assisted laser desorption/ionization-time of flight mass spectrometry (MALDI-TOF MS). 2AB-labeled GAG disaccharides were analyzed by HPLC. The glycan compositions were manually determined by conducting database searches (i.e., a compositional search of the UniCarbKB database (http://www.unicarbkb.org/query) for fOSs and N- and O-glycans and of the SphinGOMAP database (http://www.sphingomap.org/) for GSL-glycans). All previously deposited GSL-glycans in the SphinGOMAP database were extracted and compiled as an in-house database to allow searching by the m/z value and/or composition. The absolute quantification was obtained by comparative analyses between the MS signal areas derived from each glycan and the internal standard.

Statistics

All data in this study are presented as the mean ± standard deviation and were repeated at least three times unless otherwise indicated. Data analysis was performed using GraphPad Prism 9 software version 9.4.1 (GraphPad Software, Inc., San Diego, CA, USA), and the Welch t-test/Welch analysis of variance with subsequent use of the Tukey–Kramer multiple comparison tests were used to determine significant differences between the groups. P-values <0.05 were considered significant. JMP Pro version 16.2.0 (SAS Institute, Cary, NC, USA) was used to reveal the relationships between each subject of sub glycomes; we performed principal component analysis (PCA) and hierarchical cluster analysis.

Study approval

Acquisition and use of patient tissues were approved by the institutional review board (IRB) of Hokkaido University (approval number: 014-0144), and informed consent was obtained in advance. All animal studies were performed according to established ethical guidelines approved by the local animal care committee.

Supporting information

eLife Assessment

This study is valuable as it sheds light on the pivotal role played by alterations in glycan metabolism within chondrocytes in the onset of cartilage degeneration and early onset of osteoarthritis (OA) through the process of hypertrophic differentiation of chondrocytes, giving insights into the identification of nascent markers for early-stage OA. Although the methods, data, and analyses broadly support the claims, the data shown by the authors are incomplete because the mechanism by which cartilage degeneration induced by changes in glycometabolism occurs has not been fully elucidated. The authors' deductions stand to gain further credence through undertaking additional experiments aimed at analyzing the mechanisms underlying the changes in glycometabolism in cartilage, such as the meticulous identification of the target glycan molecules bearing core fucose and analysis of endochondral ossification in cartilage-specific Fut8 KO mice.

Reviewer #1 (Public Review):

Summary:

This study is valuable in that it may lead to the discovery of future OA markers, etc., in that changes in glycan metabolism in chondrocytes are involved in the initiation of cartilage degeneration and early OA via hypertrophic differentiation of chondrocytes. However, more robust results would be obtained by analyzing the mechanisms and pathways by which changes in glycosylation lead to cartilage degeneration.

Strengths:

This study is important because it indicates that glycan metabolism may be associated with pre-OA and may lead to the elucidation of the cause and diagnosis of pre-OA.

Weaknesses:

More robust results would be obtained by analyzing the mechanism by which cartilage degeneration induced by changes in glycometabolism occurs.

Reviewer #2 (Public Review):

Summary:

This paper consists of mostly descriptive data, judged from alpha-mannosidase-treated samples, in which they found an increase in core fucose, a product of Fut 8.

Strengths:

This paper is interesting in the clinical field, but unfortunately, the data is mostly descriptive and does not have a significant impact on the scientific community in general.

Weaknesses:

If core fucose is increased, at least the target glycan molecules of core fucose should be evaluated. They also found an increase in NO, suggesting that inflammatory processes also play an important role in OA in addition to glycan changes.

It has already been reported that core fucose is decreased by administration of alpha-mannosidase inhibitors. Therefore, it is expected that alpha-mannosidase administration increases core fucose.

Reviewer #3 (Public Review):

Summary:

In the manuscript "Articular cartilage corefucosylation regulates tissue resilience in osteoarthritis", the authors investigate the glycan structural changes in the context of pre-OA conditions. By mainly conducting animal experiments and glycomic analysis, this study clarified the molecular mechanism of N-glycan core fucosylation and Fut8 expression in the extracellular matrix resilience and unrecoverable cartilage degeneration. Lastly, a comprehensive glycan analysis of human OA cartilage verified the hypothesis.

Strengths:

Generally, this manuscript is well structured with rigorous logic and clear language. This study is valuable and important in the early diagnosis of OA patients in the clinic, which is a great challenge nowadays.

Weaknesses:

I recommend minor revisions:

1. I would suggest the authors prepare an illustrative scheme for the whole study, to explain the complex mechanism and also to summarize the results.

2. Including but not limited to Figures 2A-C, Figures 3A and C, Figure 4B, and Figures 5A and D. The texts in the above images are too small to read, I would suggest the authors remake these images.

3. The paper is generally readable, but the language could be polished a bit. Several writing errors should be realized during the careful check.

4. As several species and OA models were conducted in this study, it would be better if the authors could note the reason behind their choice for it.

Author Response

The following is the authors’ response to the original reviews.

eLife assessment

This study is valuable as it sheds light on the pivotal role played by alterations in glycan metabolism within chondrocytes in the onset of cartilage degeneration and early onset of osteoarthritis (OA) through the process of hypertrophic differentiation of chondrocytes, giving insights into the identification of nascent markers for early-stage OA. Although the methods, data, and analyses broadly support the claims, the data shown by the authors are incomplete because the mechanism by which cartilage degeneration induced by changes in glycometabolism occurs has not been fully elucidated. The authors' deductions stand to gain further credence through undertaking additional experiments aimed at analyzing the mechanisms underlying the changes in glycometabolism in cartilage, such as the meticulous identification of the target glycan molecules bearing core fucose and analysis of endochondral ossification in cartilage-specific Fut8 KO mice.

We wish to express our strong appreciation to the Reviewer for his or her insightful comments on our paper. We feel the comments have helped us significantly improve the paper. In particular, we wish to acknowledge the Reviewer’s highly valuable comments on the effect of Fut8 on endochondral ossification.

Reviewer #1 (Public Review): :

Summary:

This study is valuable in that it may lead to the discovery of future OA markers, etc., in that changes in glycan metabolism in chondrocytes are involved in the initiation of cartilage degeneration and early OA via hypertrophic differentiation of chondrocytes. However, more robust results would be obtained by analyzing the mechanisms and pathways by which changes in glycosylation lead to cartilage degeneration.

Strengths:

This study is important because it indicates that glycan metabolism may be associated with pre-OA and may lead to the elucidation of the cause and diagnosis of pre-OA.

We thank reviewer #1 for their interest in our work and their overall positive report.

Weaknesses:

More robust results would be obtained by analyzing the mechanism by which cartilage degeneration induced by changes in glycometabolism occurs.

To understand the mechanisms of cartilage degeneration induced by changes in glycometabolism, we attempted additional experiments using rescue experiments with external administration of TGF-β. We had shown that the addition of mannosidase to an organ culture system of normal wild-type mouse cartilage increased TGF-β gene expression from 6 hours (Fig. 3E) and that TGF-β expression was even suppressed in chondrocytes from Fut8 cKO mice (Fig. 4D). In addition to these results, an early OA model in which mannosidase is added to the cartilage was used to test the effect of exogenous TGF-β. As a result, under TGF-β treated conditions, no degenerative changes occurred when high-mannose type N-glycans were trimmed, and proteoglycan leakage during the recovery period was significantly reduced. This was considered to be a very useful finding and it was decided to include the experimental results in Figure 4F, rather than making them supplement data.

Reviewer #2 (Public Review):

Summary:

This paper consists of mostly descriptive data, judged from alpha-mannosidase-treated samples, in which they found an increase in core fucose, a product of Fut 8.

Strengths:

This paper is interesting in the clinical field, but unfortunately, the data is mostly descriptive and does not have a significant impact on the scientific community in general.

We thank reviewer #2 for their interest in our work and their overall positive report. In response to your comment about our attempts to show that glycan changes occur at the precursor stage of cartilage substrate degeneration and that this glycosylation is also what triggers substrate degeneration, we would like to add that reversing cartilage substrate degeneration is a very ambitious challenge. We are currently in the preparatory stages of characterizing the appropriate glycan-substrate relationships to 'rescue' cartilage tissue from degeneration, and we hope to use this approach to provide information on the pre-developmental stages of OA.

Weaknesses:

If core fucose is increased, at least the target glycan molecules of core fucose should be evaluated. They also found an increase in NO, suggesting that inflammatory processes also play an important role in OA in addition to glycan changes.

As the increase in NO was observed in the organ culture system and cartilage is a tissue without vascular invasion, we thought that the involvement of immune cells could be excluded. On the other hand, our research group has reported that chondrocytes themselves have inflammatory circuits (Ota et al., Arthritis Rheum. 2019. DOI:10.1002/art.41182), but as we did not find increased expression of NF-κB, an indicator of inflammatory amplifier activation, we concluded that inflammation was not involved in this study.

It has already been reported that core fucose is decreased by administration of alpha-mannosidase inhibitors. Therefore, it is expected that alpha-mannosidase administration increases core fucose.

The report by Toegel et al. that the synthesis of complex-type N-glycans (Man2a1, Mgat2) is predicted in human OA chondrocytes along with the expression of Fut8 also led to the expectation that administration of α-mannosidase would increase core fucose. However, there was no conclusive evidence that administration of α-mannosidase increased core fucose; in 1987, Vignon et al performed an enzyme assay on experimental OA cartilage (rabbit ACLT model) and showed that mannosidase was very high in operated joints and that its activity increased and decreased with the severity of fibrosis in the cartilage. The results suggest that glycoprotein hexose degradation is an early transient event in the enzymatic process of cartilage destruction. These findings led to the conception of a novel 'pre-OA model' in which mannosidase is added to the joint. The present study is valuable in its demonstration that glycometabolism is a driver of degeneration.

(see manuscript REF. 25, 9)

Toegel et al., Arthritis Res. Ther. 2013. DOI:10.1186/ar4330

Vignon et al., Clin Rheumatol. 1987. DOI:10.1007/BF02201026

Reviewer #3 (Public Review):

Summary:

In the manuscript "Articular cartilage corefucosylation regulates tissue resilience in osteoarthritis", the authors investigate the glycan structural changes in the context of pre-OA conditions. By mainly conducting animal experiments and glycomic analysis, this study clarified the molecular mechanism of N-glycan core fucosylation and Fut8 expression in the extracellular matrix resilience and unrecoverable cartilage degeneration. Lastly, a comprehensive glycan analysis of human OA cartilage verified the hypothesis.

Strengths:

Generally, this manuscript is well structured with rigorous logic and clear language. This study is valuable and important in the early diagnosis of OA patients in the clinic, which is a great challenge nowadays.

We thank reviewer #3 for their interest in our work and their mainly positive report. This is precisely the purpose of our study, as we are primarily interested in the detection of conditions prior to the onset of OA.

Weaknesses:

I recommend minor revisions:

(1) I would suggest the authors prepare an illustrative scheme for the whole study, to explain the complex mechanism and also to summarize the results.

We would like to thank the reviewer for this comment and have created a new Figure 7 for the overall study scheme.

We included the following statement in the opening discussion part:

"The objective of this work was to provide novel and translational insights into pathogenesis of OA associated with changes in glycan structure. A graphical abstract summarizing our findings is shown in Fig. 7." (line199-201, p9)

(2) Including but not limited to Figures 2A-C, Figures 3A and C, Figure 4B, and Figures 5A and D. The texts in the above images are too small to read, I would suggest the authors remake these images.

The font size of the figures has been reviewed and revised throughout.

(3) The paper is generally readable, but the language could be polished a bit. Several writing errors should be realized during the careful check.

Thanks to your suggestion, I have noticed several writing errors. In addition, we have had the manuscript rewritten by an experienced scientific editor, who has improved the grammar and stylistic expression of the paper.

(4) As several species and OA models were conducted in this study, it would be better if the authors could note the reason behind their choice for it.

The authors agree with the reviewer's argument that since several species and OA models were performed in this study, it would be better to note the reason for their choice.

We first attempted to inject mannosidase into rabbits, matching the animal species to a previous paper showing that N-glycans are altered prior to degeneration of the cartilage matrix. Next, we checked whether similar changes occur in mouse cartilage after mannosidase treatment, assuming that we would verify this in genetically engineered mice. We then used the integrated glycome in human cartilage to see if the corefucosylation phenomenon detected was conserved across species.

For the modeling of OA in Fut8 cKO mice, the instability-induced OA model and the age-associated OA model were adapted. The former emphasizes mechanical stress factors in OA, the latter aging factors. OA is a multifactorial disease. Therefore, we thought it was appropriate to validate both aspects of OA.

We included the following statements in each Methods part:

"We injected mannosidase into rabbit knee joints in accordance with a previous paper showing that N-type glycans are altered prior to cartilage matrix degeneration." (line289-290, p12)

"Organ culture experiments in mice were established to study the effects of mannosidase on articular cartilage without immunoreaction and in anticipation of later candidate gene research using transgenic mice." (line326-328, p14)

"To determine whether the glycosylation detected is conserved across species, we analyzed the total glycome in human cartilage." (line407-408, p17)

We included the following statements in the Discussion part:

"For the modeling of OA in Fut8 cKO mice, the instability-induced OA model and the age-associated OA model were adapted. The former emphasizes mechanical stress factors in OA, the latter aging factors. OA is a multifactorial disease. Therefore, we thought it was appropriate to validate both aspects of OA." (line254-257, p11)

Reviewer #1 (Recommendations For The Authors):

(1) The cited literature states that core fucosylation by FUT8 has a chondroprotective effect via the TGF-β pathway and that the loss of these chondroprotective effects in Fut8 led to cartilage degeneration, but these need to be proven by experiment.

We agree that corefucosylation and the TGF-β signaling pathway are important lines of investigation. We have now acknowledged this and added in the revised manuscript that additional experiments have shown that TGF-β restores the protective effects of Fut8 cKO cartilage by external administration.

We included the following statements in the Results part:

"To evaluate whether TGF-β1 decreases cartilage degeneration after mannosidase stimulation, TGF-β1 was exogenously added to Col2-Fut8−/− cartilage in the presence of α-mannosidase stimulation for 24 h. The samples treated with TGF-β1 leaked significantly less PG following mannosidase stimulation compared to samples not treated with TGF-β1 (Fig. 4F)." (line143-147, p6-7)

We included the following statements in the Discussion part:

"Here, the exogenous addition of TGF-β1 rescued them from cartilage degeneration." (line274-275, p12)

(2) There are skeletal differences in cartilage-specific Fut8 KO mice compared to WT, and the effect of Fut8 on endochondral ossification should also be analyzed.

We agree that Fut8 is associated with various endochondral ossification processes (for example by the TGF-β signaling pathway). Moreover, we would like to thank the reviewer for the proposed experiment.

The growth curve was normal at birth, with differences beginning around weaning (~3 w for mice). Therefore, we evaluated the epiphyseal line of 4-week-old mice stained with toluidine, type 10 collagen, and proliferating cell nuclear antigen. This is similar to the epiphyseal growth plate phenotype of Smad3ex8/ex8 mice by Yang et al. and is consistent with the finding that Smad3 deficiency does not affect chondrogenesis during developmental stages, but the hypertrophic zone is increased in 3-4 week-old Smad3 KO mice. Chondrocytes in Fut8 cKO mice were suppressed of Tgf-β expression (Fig. 4D), suggesting that inhibition of TGF-β signaling, which is suppressive for late hypertrophic chondrocyte differentiation, led to the increased height of the hypertrophic zone.

The results suggested that the growth plate of Fut8 cKO mice had an enlarged hypertrophic layer and decreased primary trabecular bone. Because these results have important implications for the content of the paper, we have included the staining results in Figure 5 and added a graph quantitatively assessing the extent of the hypertrophic zone as supplementary Figure S6.

We included the following statement in the Results part:

"To assess the role of FUT8 in endochondral ossification, we performed an epiphyseal plate analysis of 4-week-old Col2-Fut8−/− mice. This uncovered a significant enlargement of the zone of hypertrophic chondrocytes in the growth plates of the long bones of Col2-Fut8−/− mice compared to controls (Fig. 5C, S6 Figure)." (line154-158, p7)

We included the following statement in the Discussion part:

"The high-mannose/corefucosylation relationship estimated function to maintain formed cartilage. In endochondral ossification, the Fut8 cKO growth plate had an enlarged hypertrophic zone and reduced primary spongiosa because it is involved in the next process of cartilage replacement into bone rather than the process of cartilage formation." (line214-217, p9)

Literature mentioned above (not included in manuscript):

Yang X, et al. TGF-beta/Smad3 signals repress chondrocyte hypertrophic differentiation and are required for maintaining articular cartilage. J Cell Biol. 2001;153(1):35–46.

(3) The DMM model analysis is performed with n=5 for each group. Please consider if the sample size is sufficient.

In the literature, the sample sizes for DMM models have varied in previous studies (Doyran et al., n=5; Liao et al., n=6-7; Ouhaddi et al., n=8). Therefore, we performed a preliminary test of the DMM in WT and Flox mice with n=3 each and a power analysis with the outcome set to the OARSI score at 8 weeks. This resulted in n=4. The sample size for this study was increased to n=5 to account for attrition. The summed OARSI score of the WT in this study was comparable to that of Ouhaddi et al. and the model was judged to be working accurately. The summed OARSI score of the WT in this study was comparable to that of Ouhaddi et al. and the model was judged to be working accurately. The summed OARSI score of the WT in this study was comparable to that of Ouhaddi et al. and the model was judged to be working accurately.

Literature mentioned above (not included in manuscript):

(1) Doyran B, Tong W, Li Q, Jia H, Zhang X, Chen C, et al. Nanoindentation modulus of murine cartilage: a sensitive indicator of the initiation and progression of post-traumatic osteoarthritis. Osteoarthr Cartil. 2017;25(1):108–17.

(2) Liao L, Zhang S, Gu J, Takarada T, Yoneda Y, Huang J, et al. Deletion of Runx2 in Articular Chondrocytes Decelerates the Progression of DMM-Induced Osteoarthritis in Adult Mice. Sci Rep. 2017 24;7(1):2371.

(3) Ouhaddi Y, Nebbaki SS, Habouri L, Afif H, Lussier B, Kapoor M, et al. Exacerbation of Aging-Associated and Instability-Induced Murine Osteoarthritis With Deletion of D Prostanoid Receptor 1, a Prostaglandin D2 Receptor. Arthritis Rheum. 2017;69(9):1784–95.

Reviewer #2 (Recommendations For The Authors):

This paper is suitable for publication in clinical Journals related to osteoarthritis and cartilage.

Identification of core fucosylated glycans from chondrocytes is essential for this type of paper.

We mentioned that we had identified similar corefucosylated glycans in isolated mouse chondrocytes from the cartilage (line117-118, p5), but we have now also added the following to the subtitle of the Results section to avoid any potential confusion: "Corefucosylated N-glycan was formed in resilient cartilage and its isolated chondrocyte" (line109, p5)

Thank you again for your comments on our paper. We trust that the revised manuscript is suitable for publication.

Version 2

Abstract

Abstract

This study aimed to investigate the glycan structural changes that occur before histological degeneration in osteoarthritis (OA) and to determine the mechanism by which these glycan conformational changes affect cartilage degeneration. An OA model was established in rabbits using mannosidase injection, which reduced high-mannose type N-glycans and led to cartilage degeneration. Further analysis of glycome in human OA cartilage identified specific corefucosylated N-glycan expression patterns. Inhibition of N-glycan corefucosylation resulted in unrecoverable cartilage degeneration, while cartilage-specific blocking of corefucosylation led to accelerated development of aging-associated and instability-induced OA models. We conclude that α1,6 fucosyltransferase is required postnatally to prevent preosteoarthritic deterioration of articular cartilage. These findings provide a novel definition of early OA and identify glyco-phenotypes of OA cartilage, which may distinguish individuals at higher risk of progression.

Introduction

Osteoarthritis (OA), a degeneration of joint components, such as proteoglycans (PGs) and collagen, destroys cartilage and impairs joint function (1). The global prevalence of OA is estimated to be >500 million, which is a significant socioeconomic burden (2). Therefore, preventive measures must be implemented to reduce the future disease burden and disability. Once the cartilage is destroyed, it cannot be repaired homogeneously and progresses irreversibly thereafter (3, 4). Since articular cartilage has no blood vessels and is not innervated, it is difficult for symptoms to appear. By the time clinical symptoms appear, the condition is often already considerably advanced (5). Therefore, from a preventive perspective, it is necessary to define and detect “pre-OA,” the stage before the onset of early OA (6, 7). Pre-OA is a knee with no pain, no motor function problems, and no arthroscopic or structural changes on radiography, only emerging cellular effects. Despite many studies, there is no gold standard for OA biomarkers (8). It is important to characterize the disease state before OA to shift the paradigm from mitigation to late-onset disease prevention.

In the very early stages of OA, before cartilage matrix degeneration, cartilage destruction by enzymatic processes that degrade glycoproteins, PGs, and collagen, in that order, is underway (9). Collagenolytic activity is largely unchanged on intact articular surfaces (10, 11), and glycoprotein degradation is thought to be an early transient event in the enzymatic process of cartilage destruction because hexose degradation of glycoproteins promotes degradation of the protein portion of the molecule by proteinases (12). Additionally, cartilage damage is reversible if type 2 collagen breakdown is mild (13). Structural change analysis in glycoproteins is necessary for the early stages of OA but has not yet been performed sufficiently.

Matsuhashi et al.’s study showed that structural changes in N-glycans occurred in degenerated cartilage in a rabbit OA model before tissue changes occurred (14). Urita et al. demonstrated that these N-glycans in degenerated mice and human cartilage are high-mannose type N-glycans (15). Furthermore, among several glycosidases, mannosidase activity was very high in OA joints, and its activity was high before the progression of cartilage fibrosis (16). This suggests that high-mannose type N-glycan plays an important role in OA pathogenesis. However, whether changes in the glycan structure are involved in OA pathogenesis is unclear.

This study analyzed the glycan structural changes that preceded OA degeneration and elucidated the mechanism of glycan structural changes in cartilage degeneration. For this purpose, the effects of mannosidase, a specific degrading enzyme of high-mannose type N-glycans associated with OA, on cartilage tissues and its molecular mechanisms were analyzed.

Results

Mannosidase injection caused early OA-like change in vivo

A decrease in Safranin O staining in the right femoral condyle of the α-mannosidase-injected knee after 4 weeks was observed (Fig. 1A, B). Terminal deoxynucleotidyl transferase dUTP nick end labeling (TUNEL) staining was enhanced in the superficial layer compared with that in control. Articular cartilage chondrocytes exposed to α-mannosidase were not arranged in columns in the middle zone. The surfaces of each group were smooth and had a good macroscopic appearance (Fig. 1C). None of the groups showed a decrease in type 2 collagen staining, and the orientation was maintained (Fig. 1D). To achieve optimal activity, the pH range of 4 to 5 is ideal for mannosidase. In a physiological saline solution with a pH of 7 and a concentration of 100 μg/ml, it exhibited specific activity. Nevertheless, at a concentration of 1.0 μg/ml, this activity was no longer present (S1 Figure). The mean histological score of the α-mannosidase group was 0.83, indicating mild OA (Fig. 1E). The control group was unchanged. Cartilage degeneration during intermittent intra-articular administration of mannosidase was reversed upon discontinuation (Fig. 1F).

Effects of α-mannosidase injection in the knee joint in vivo.

(A) Time course of intra-articular α-mannosidase injection and unloading. Red arrows indicate the one-shot, intra-articular injection that was performed once a week. (B) Histological evaluation of knee articular cartilage 4 weeks after intermittent α-mannosidase infusion and 16 weeks after load removal. Scale bars, 50 μm. (C) Representative macroscopic assessment of the articular cartilage using mannosidase concentration. Scale bar, 1 cm. (D) Evaluation of the collagen orientation of reparative tissues at 4 weeks postoperatively. Sections stained with HE was viewed under a polarized light microscope at multiple angles (0°, 45°, and 90°). Scale bar, 200 μm. (E) OARSI scores at 4 weeks postoperatively on sections from the knee joint (n = 6). (F) Tissue degeneration scores at each time point are based on mannosidase concentration. Data are shown as mean ± standard deviation. *P < 0.05, **P < 0.01 versus the saline group in (E), and versus 4 weeks in (F). In (E), the Welch t-test was used for statistical analysis. In (F), n = 6 rabbits per group. One-way analysis of variance with Tukey’s multiple comparison test was used to perform statistical analysis. HE, hematoxylin and eosin; OARSI, Osteoarthritis Research Society International; TUNEL, terminal deoxynucleotidyl transferase dUTP nick end labeling.

Depletion of high-mannose type N-glycans in chondrocytes leads to cartilage degradation ex vivo

To quantify the degeneration and resilience promoted by the injection of α-mannosidase, the cultured cartilage was harvested at different time points (Fig. 2A). Concanavalin A (Con A) reactivity declined in articular cartilage treated with α-mannosidase (Fig. 2B). The application of α-mannosidase stimulated the release of PG from cultured cartilage in association with extracellular matrix degradation (Fig. 2C) and showed significantly higher spontaneous nitric oxide (NO) release than the control over time (Fig. 2F). Mannosidase-exposed cartilage showed an increase in TUNEL-positive cells in chondrocytes in the deep zone and type 10 collagen-positive cells in superficial chondrocytes; however, these changes did not occur in cytokine-stimulated cartilage (S2 Figure). Mannosidase exposure increased Adamts5 expression and suppressed Mmp13 expression and anabolic factors (Fig. 3E). In the articular cartilage that was exposed to freeze-thaw treatment before culture, no differences in PG loss were observed between the α-mannosidase-stimulated cartilage and non-stimulated cartilage (Fig. 2E). Excluding mannosidase loading, PG leakage and Safranin O staining were restored (Fig. 2D), but Con A staining loss was not. Sialidase addition did not cause PG leakage or NO production (S3 Figure), and the aggrecan lost in the catabolic phase was not replenished in the subsequent anabolic phase.

Cartilage degradation induced by mannosidase stimulation.

(A) Schematic diagram of the procedures used to establish the early OA model before irreversible and progressive destruction of articular cartilage. (B) Mannosidase-treated cartilage stained with Safranin O and Con A. The distribution of high-mannose type N-glycans is decreased in mannosidase-induced degraded mouse cartilage. Scale bars, 50 μm. (C), (D) PG release after exposure to mannosidase (C) and recovery after its removal from cultured cartilage grafts (D). (E) To investigate the non-chondrocyte-mediated release of fragments, PG loss was measured in cartilage explants that had undergone freeze-thaw cycles. (F) Sequential NO released into media measured as concentrations of nitrite for cartilage explants stimulated with mannosidase. Data are shown as mean ± standard deviation (s.d.). *P < 0.05, **P < 0.01 versus the control group in (C), (E), and (F), and versus day 3 in (D). In (C) and (E), n = 3 samples (six mice) per group. One-way ANOVA with the Tukey multiple comparison test was used to perform statistical analysis. In (D), n = 12 mice in each group and n = 3 samples (six mice) at each time point. In (F), n = 16 mice at each time point and n = 4 samples (eight mice) per group. In (D) and (F), two-way ANOVA with the Sidak multiple-comparisons test was used to perform statistical analysis. Con A, concanavalin A; NO, nitric oxide; ANOVA, analysis of variance; PG, proteoglycan.

Cartilage N-glycomes.

(A) MALDI-TOF MS spectra showing the quantitative N-glycan profiles of cartilage before (upper) and after (lower) mannosidase treatment. (B) Scatter plot of the changes in m/z per protein abundance in the mannosidase (x-axis) and control (y-axis) N-glycan structures. The red dots indicate the top 10 N-glycan structures based on the deviation from the y = x line. (C) Heatmap of N-glycome showing differential N-glycan expression in the mannosidase (man+) group versus the control (man-) group. (D) N-glycans altered by mannosidase were corefucosylated glycans and high-mannose type N-glycans. (E) RT-PCR expression analysis of marker genes in organ culture of cartilage with mannosidase. Data are shown as mean ± standard deviation. *P < 0.05, **P < 0.01 versus the control group in (D), and versus 0 hours in (E). In (D) and (E), n = 3 samples (six mice) per group. In (D), unpaired t-tests were used to perform statistical analyses. In (E), one-way ANOVA with the Dunnett multiple comparison test was used to perform statistical analysis. MALDI-TOF MS, matrix-assisted laser desorption/ionization-time of flight mass spectrometry; ANOVA, analysis of variance; RT-PCR, real-time polymerase chain reaction.

Corefucosylated N-glycan was formed in resilient cartilage and isolated chondrocyte

Glycoblotting analysis revealed a significant difference in the N-glycan profiles (Fig. 3A and S1 Table). Plotting m/z after mannosidase exposure against m/z before mannosidase exposure demonstrated that only N-glycans were affected by enzyme dissociation from the y = x line (Fig. 3B, S2 Table). In both denatured and reverted cartilages, Man8-9GlcNAc2 was decreased, and Man5-6GlcNAc2 was increased by the action of mannosidase, which has a high specificity for the terminal mannosidic residues of glycans (Fig. 3C, D). In contrast, corefucosylated N-glycans, which were formed in the same biosynthesis pathway, were also found (Fig. 3D). Similarly, the N-glycan profiles of isolated chondrocytes showed the presence of this corefucosylated structure (S4 Figure). The expression of Fut8, the only enzyme involved in corefucosylation, increased significantly in mannosidase-treated cartilage (Fig. 3E).

Deficiency of corefucosylated glycans in articular cartilage inhibits recovery from cartilage damage and promotes cartilage degeneration

We first examined whether the absence of core fucose affects the resilience of cartilage degeneration. Mice lacking Fut8 exhibited severe growth retardation and died shortly after birth. Therefore, we decided to generate Fut8 conditional knockout (cKO) mice (Fig. 4A, B). The tissue specificity of recombination was confirmed by polymerase chain reaction (PCR) analysis of mouse genomic DNA that detected either the intact Fut8loxP allele or the Cre-recombined Fut8Δ allele in repeated crosses; N-glycan analysis of cartilage demonstrated the loss of corefucosylated sugar chains (Fig. 4C). The proportion of high-mannose type N-glycan content was unchanged in cartilage lacking the Fut8 gene (S5 Figure). Next, we used real-time (RT)-PCR to determine relative Fut8 messenger (m)-RNA levels in the cartilage of Col2-Fut8−/− mice and their wild-type (WT) littermates (Fut8loxP/loxP). Real-time polymerase chain reaction (RT-PCR) analysis showed that Fut8 mRNA expression was reduced by >99% in the articular cartilage of Col2-Fut8−/− mice compared to that in their WT littermates (P < 0.01; n = 3 mice per group) (Fig. 4D). Chondrocyte-surface corefucosylation levels were analyzed by lectin staining using Pholiota squarrosa lectin (PhoSL), which specifically recognizes α1-6 core fucose (17). PhoSL lectin staining was completely absent in the articular cartilage of Fut8 cKO mice, in contrast to the positive staining observed in Fut8 flox mice under physiological conditions (Fig. 4E). Enzymatic degradation of high-mannose type N-glycans on the cartilage in Fut8-deficient mice exacerbated cartilage degeneration (Fig. 4E, F). In addition, reversible matrix repair by enzyme removal observed in control cartilage was not observed in Fut8-deficient cartilage explant cultures. To evaluate whether TGF-β1 decreases cartilage degeneration after mannosidase stimulation, TGF-β1 was exogenously added to Col2-Fut8−/− cartilage in the presence of α-mannosidase stimulation for 24 h. The samples treated with TGF-β1 leaked significantly less PG following mannosidase stimulation compared to samples not treated with TGF-β1 (Fig. 4F).

Loss of resilience due to FUT8 deficiency in cartilage.

(A) Biological reaction of FUT8. FUT8 transfers fucose to the innermost GlcNAc residue of complex N-glycans via α1,6-linkage (corefucosylation). (B) Targeted disruption of Fut8 locus. The Fut8 gene (WT allele; top), targeting vector (middle), and disrupted Fut8 locus (mutant allele; bottom). Schematic representation of the Fut8-targeting strategy and Cre-mediated recombination of the Fut8loxP allele. (C) MALDI-TOF MS mass spectra of N-glycans from WT and Fut8 cKO mice. The corefucosylation levels in cartilage were decreased and undetectable in Fut8 cKO mice. (D) Gene profile in chondrocytes isolated from Fut8 cKO mice. The expression levels of these genes in WT cells were set to 1. PPIA, peptidylprolyl isomerase A. (E) Histological findings in cartilage explants from Fut8 cKO mice and their floxed littermates cultured with mannosidase and subjected to Safranin O staining and PhoSL lectin staining. Scale bar, 50 μm. (F) PG release in cultured cartilage explants from Fut8 cKO mice and their floxed littermates. M-, Mannosidase (-); M+, Mannosidase (+). Data are shown as mean ± standard deviation. In (F), n = 3 samples (six mice) per group. *P < 0.05, **P < 0.01. One-way ANOVA, with the Tukey multiple comparison test, was used to perform statistical analysis. MALDI-TOF MS, matrix-assisted laser desorption/ionization-time of flight mass spectrometry; WT, wild-type; cKO, conditional knockout; PG, proteoglycan; ANOVA, analysis of variance.

Loss of corefucosylated glycans in articular cartilage leads to premature OA

Col2-Fut8−/− mice developed and grew normally without major organ abnormalities of major organs and could not be distinguished from their WT littermates. The whole skeletons of newborn mice stained with alcian blue and alizarin red did not differ in appearance between the genotypes (Fig. 5A). Col2-Fut8−/− mice showed a lower body weight than their WT littermates, as indicated by the growth curve (Fig. 5B). To assess the role of FUT8 in endochondral ossification, we performed an epiphyseal plate analysis of 4-week-old Col2-Fut8−/− mice. This uncovered a significant enlargement of the zone of hypertrophic chondrocytes in the growth plates of the long bones of Col2-Fut8−/− mice compared to controls (Fig. 5C, S6 Figure). We analyzed the development of instability-induced OA changes in Fut8loxP/loxP and Fut8 cKO mice. Sham operations produced no significant changes in OA in either mouse genotype. Eight weeks after instability-inducing surgery, the joints of WT mice developed changes in OA, such as cartilage erosion and a reduction in Safranin O staining and chondrocyte number. Deletion of FUT8 results in more severe changes in OA. In the joints of Fut8 cKO mice, 8 weeks after surgery, the noncalcified zone (the upper layer above the tidemark) was almost completely lost. The number of chondrocytes was significantly reduced (Fig. 5D). Quantitative assessment using the OA Research Society International (OARSI) score supported these histological findings (difference: -2.900; Fut8flox/flox/destabilization of the medial meniscus (DMM) versus Col2a1-Cre; Fut8flox/flox/DMM, 95% confidence interval [CI] for the difference: -5.027 to -0.7734) (Fig. 5E). Changes in OA progressed earlier in the aging models of Fut8-deficient mice than in control mice (WT and floxed mice). The mice were followed up until 15 months of age to assess the spontaneous development of OA with aging (Fig. 5F). There were no apparent changes of OA in the knee joints of either mouse genotype at 3 months of age (Fig. 5G). At 4 months of age, significant changes in OA were detected in the knee joints of the Fut8 cKO mice. The cartilage surface integrity was no longer maintained at 9 months. These OA changes progressed more in Fut8 cKO mice than in their WT littermates at 15 months. These histological findings were quantitatively confirmed by the Osteoarthritis Research Society International (OARSI) scores (difference: -2.000; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -3.723 to -0.2771 at 4 months, difference: -2.700; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -4.423 to -0.9771 at 9 months, and difference: -6.700; WT versus Col2a1-Cre; Fut8flox/flox, 95% CI for the difference: -8.423 to -4.977 at 15 months).

OA acceleration in Fut8 cKO mice.

(A) Double staining with alizarin red and alcian blue of the whole skeleton of wild-type and Col2a1-Cre;Fut8flox/flox cKO littermate embryos (newborn). Scale bars, 1 cm (left). Weight and body length of wild-type and cKO littermate embryos (right). (B) Growth curves were determined by body weight in male (left) and female (right) wild-type mice and their cKO littermates. (C) Histologic findings in knee joints from 4-week-old mice. Toluidine blue (TB) staining and immunostaining for type X collagen (Col10) and proliferating cell nuclear antigen (PCNA) in growth plates of the tibia were performed in each mouse genotype. The dashed line indicates the hypertrophic zone. Scale bar, 100 μm. (D), (E) Features of instability-induced OA in Fut8flox/flox (flox) mice and their cKO littermates 8 weeks after surgery. Safranin O staining is shown for each mouse genotype. Scale bar, 100 μm (D). Summed histological scores for OA severity in the knee cartilage from flox and cKO mice, as determined using the OARSI scoring system, are shown (E). (F), (G) Features of age-associated osteoarthritis in wild-type mice and their flox and cKO littermates. Safranin O staining of the knee joint is shown for each mouse genotype at 3, 4, 9, and 15 months of age. Scale bar, 100 μm (F). The summed OARSI scores are shown (G). Data are shown as mean ± standard deviation. In (A), the Welch t-test was used to perform statistical analyses (n = 6 mice per group). In (B), n = 15 mice per group at each time point. In (E) and (G), n = 5 mice per group at each time point. *P < 0.05, **P < 0.01 versus the wild-type group in (B) and (G), and versus flox mice in (E). One-way ANOVA with the Tukey multiple comparisons test (B), and two-way ANOVA with the Tukey multiple comparisons test (E and G) were used to perform statistical analysis. OA, osteoarthritis; cKO, conditional knockout; OARSI, Osteoarthritis Research Society International. ANOVA, analysis of variance; ns, not significant.

Altered glycosylation of human OA cartilage based on comprehensive glycan analysis

Total glycome profiling of human OA cartilage is shown in Fig. 6A and S3 Table. The amount of high-mannose type N-glycan was significantly decreased, the same as previously reported in OA cartilages (Fig. 6A) (15). Focusing on fucosylation, most of the complex/hybrid type glycans were modified with fucose. The fucosylation that occurs at the innermost N-acetylglucosamine (GlcNAc) of N-glycans could be recognized with a lectin from the mushroom Pholiota squarrosa (PhoSL) and was able to detect the expression of the corefucose structure. Therefore, we suspected that the stainability of PhoSL is increased in OA cartilage. As expected, the PhoSL staining of OA cartilage was significantly increased relative to that of a healthy control (Fig. 6B). We performed principal component analysis (PCA) on 1110 glycomic data, discriminating OA from healthy cartilages along the first principal component (PC1) axis (Fig. 6C). Hierarchical cluster analysis showed that clades containing corefucosylated glycans were clustered (Fig. 6D), and N-13 ((Hex)1 (HexNAc)1 (Fuc)1 + (Man)3(GlcNAc)2) has the largest squared correlation with its cluster component.

Altered glycosylation of human Osteoarthritis (OA) cartilage based on comprehensive glycan analysis.

(A) Total glycome profiling of human OA cartilage. Pie charts at the vertices of the pentagon correspond to the glycan expression profiles of N-glycans, O-glycans, GSL-glycans, free oligosaccharides (fOS), and glycosaminoglycan (GAG). The size of each circle and its constituent colors reflect the absolute quantity of glycans (pmol/100 μg protein) and the glycan substructures, respectively. The sizes of the circles representing the GAG contents are decreased by 1/10-fold. Each color indicates the estimated glycan structure and corresponds to the respective glycan number in the S3 Table. (B) Expression of core fucose in healthy and OA cartilage. Scale bar, 100 μm. (C) Principal component analysis (PCA) of a glycan expression data set. Data points represent individual samples. The first principal component (PC1) distinguishes healthy and OA samples. (D) Hierarchical cluster analysis results showing cluster image display for total glycans with color gradient for relative glycan expression and dendrogram for each glycan structure. Cluster summary of PCA on the glycome are shown on the right. The most representative variable is (Hex)1 (HexNAc)1 (Fuc)1 + (Man)3(GlcNAc)2 which means the largest squared correlation with its cluster component.

Discussion

The objective of this work was to provide novel and translational insights into the pathogenesis of OA associated with changes in glycan structure. A graphical abstract summarizing our findings is shown in Fig. 7. To test the hypothesis that structural changes in high-mannose type N-glycans may induce OA, we tested the effect of mannosidase loading on the structure of high-mannose type N-glycans. Consequently, modifying the structure of high-mannose type N-glycans by mannosidase loading induced OA-like histological alterations. Furthermore, the OA-like changes induced by mannosidase were recovered by enzyme removal. These results suggest that structural alterations of high-mannose type N-glycans lead to OA-like histological changes in articular cartilage but do not necessarily cause the pathogenesis of eventual OA. Subsequently, glycoblotting analysis revealed that core-fucose-containing glycans underwent complementary structural alterations per high-mannose type N-glycans. This suggests that the structural change of core-fucose-containing glycans may have some compensatory mechanism for OA-like alterations caused by the structural change of high-mannose type N-glycans. Furthermore, under the regulation of Fut8 expression, which regulates the synthesis of core fucose, mannosidase was found to induce irreversible OA. The high-mannose/corefucosylation relationship estimated function to maintain formed cartilage. In endochondral ossification, the Fut8 cKO growth plate had an enlarged hypertrophic zone and reduced primary spongiosa because it is involved in the next process of cartilage replacement into bone rather than the process of cartilage formation. These results provide the first evidence that structural alterations in glycans in the articular cartilage regulate eventual OA development.

Graphical abstract.

The corefucosylation of N-glycans is associated with the reduction of high-mannose type N-glycans in articular cartilage functions to maintain the formed vitreous cartilage as cartilage. Failure of the complementary relationship leads to irreversible cartilage degeneration and destruction of cartilage integrity.

Two key targets of cartilage degeneration during OA are type II collagen, a major substrate of matrix metalloproteinase (MMP)-13 (18), and aggrecan, a PG with glycosaminoglycan side chains of chondroitin and keratin sulfate (19, 20). The degradation of non-collagenous molecules, such as aggrecan, occurs before the degradation of type II collagen in the early stages of OA (20, 21). The histological analysis in this study revealed that the alteration in the structure of high-mannose type N-glycans resulted in a decrease in Safranin O staining (a decrease in glycosaminoglycans and/or PGs), whereas there was no change in collagen staining. These findings are consistent with alterations in the early stages of OA. Furthermore, we observed that removing mannosidase could cause PG loss to the control level. Karsdal et al. demonstrated that articular cartilage degradation is reversible in the presence of aggrecanase and concluded that the repair ability is not impaired before the degradation of aggrecan and type II collagen by MMPs (22). Reimann et al. observed that the glycosaminoglycans loss in articular cartilage is reversible and an early sign of OA before the “state of no return.” (23) The present results are consistent with the findings of previous reports on early OA and suggest that the mannosidase-loaded model can be considered an early OA-like alteration.

Since the structural change in high-mannose type N-glycans alone did not cause irreversible OA, we investigated other regulatory mechanisms related to high-mannose type N-glycans that could induce irreversible OA. The expression of corefucosylated N-glycans on a series of biosynthetic pathways was upregulated with structural changes in high-mannose type N-glycans. FUT8 is known to corefucosylate small oligomannose N-glycans (Man4-Man5GlcNAc2) but not large oligomannose N-glycans, such as Man8-Man9GlcNAc2 (24). This suggests that small oligomannose N-glycans trimmed by mannosidase could activate Fut8. Fut8 is also upregulated in human OA chondrocytes (25, 26), and increased expression of these corefucosylated N-glycans has been observed during late chondrocyte differentiation (27). These findings suggested that these structural changes are related to OA-related glycosylation.

To clarify the relationship between the alteration of corefucosylated N-glycans and cartilage degeneration, Fut8 cKO mice were used. Since the results of the ex vivo freeze-thaw model showed that cartilage degeneration was induced by changes in the glycan structure of chondrocytes, we used chondrocyte-specific KO mice. As a result, the reversibility of the cartilage degeneration model was diminished. This finding suggests that Fut8-mediated corefucosylation in chondrocytes plays a function in promoting glycan repair. Furthermore, to directly determine whether Fut8 was involved in the inhibition of OA progression, the OA model was investigated. For the modeling of OA in Fut8 cKO mice, the instability-induced OA model and the age-associated OA model were adapted. The former emphasizes mechanical stress factors in OA, the latter aging factors. OA is a multifactorial disease. Therefore, we thought it was appropriate to validate both aspects of OA. The results showed that conditional KO of Fut8 in chondrocytes hastened the onset of OA. This suggests that cartilage corefucosylation associated with FUT8 plays a protective role against the attenuation of type II collagen in the OA process.

Finally, the expression of α1,6-linked core fucose on N-glycans in human cartilage is associated with OA, and corefucosylation was found to be one of the characteristics in OA cartilage. Total cellular glycome analysis, including N- and O-linked glycans derived from glycoproteins, GSL-glycans, GAGs, and fOSs, is informative for analyzing cell-specific characteristics (28‒30). Glycome profiling enabled the detection of corefucosylated N-glycans by sequential clustering of degenerated cartilage characteristics. Core fucose deficient mice generated by ablating the α1,6 fucosyltransferase enzyme, FUT8, were reported to have suppressed phosphorylation of Smad and increased expression of MMPs (matrix metalloproteinases) due to decreased binding of TGF-β ligand caused by the lack of core fucose addition to the TGF-β type II receptor (31, 32). The present study shows that treatment of cartilage with mannosidase caused corefucosylation, suppression of Mmp13, and increased expression of Tgf-β. Moreover, treatment of FUT8-knockout cartilage with mannosidase resulted in the suppression of Tgf-β expression and increased Mmp13 expression. Here, the exogenous addition of TGF-β1 rescued them from cartilage degeneration. These results suggest that corefucosylation following the loss of high-mannose type N-glycans may provide chondroprotective effects via the TGF-β signaling pathway, which may have been lost by FUT8-knockout.

One limitation of this study was that we did not have access to cartilage samples from immediately before the onset of OA; thus, we do not know the expression of Fut8 in human cartilage in the early stage of OA onset and its influence on extracellular matrix degradation under homeostatic conditions. Obtaining cartilage specimens continues to be challenging, especially for those with early stages of OA.

In summary, we show for the first time a key role of FUT8 and glycan-dependent signaling mediators in extracellular matrix resilience associated with cartilage corefucosylation during early OA.

Methods

Intra-articular injection of α-mannosidase in the knee

We injected mannosidase into rabbit knee joints in accordance with a previous paper showing that N-type glycans are altered prior to cartilage matrix degeneration. Japanese White rabbits weighing 3.10 ± 0.15 kg purchased from a professional breeder (Japan SLC Inc., Hamamatsu, Japan) were used for this study according to established ethical guidelines approved by the local animal care committee. Animals were anesthetized with 10 mg/kg of intravenous ketamine, followed by isoflurane in oxygen gas. Both knees in each rabbit were shaved, prepared, and draped in a sterile fashion. α-Mannosidase from Canavalia ensiformis (Jack bean) (Sigma, St Louis, MO, USA) was dissolved in saline. Five hundred microliter volumes containing 1.9 units per ml (0.05 mg) of mannosidase solution were injected into the joint cavity of the right knee. α-Mannosidase from Canavalia ensiformis (Jack bean) has been widely used as a tool for glycan analysis, which has a high specificity towards terminal mannosidic residues of glycans and participates in mannose trimming reactions (33). The measurement of its performance in a saline solution was evaluated using the QuantiChrom α-Mannosidase Assay Kit (BioAssay Systems, Hayward, CA, USA). This colorimetric assay uses 4-nitrophenyl-α-d-mannopyranoside as a substrate to identify the generation of 4-nitrophenol. The following doses of α-Mannosidase were administered: 0.5 ml at 0.01 μg/ml, 1.0 μg/ml, or 100 μg/ml. Simultaneously, the contralateral knee joint received an equal volume of saline solution. Each joint was injected once or four times in alternate weeks. The animals were euthanized at 4 and 16 weeks postoperatively. Each section of the knee joint was stained with hematoxylin and eosin or Safranin O/fast green, as well as with immunohistochemical staining for type II collagen and TUNEL. Two investigators quantified the OA severity using the OARSI scoring method.

Evaluation of collagen orientation by a polarized light microscope

To evaluate the collagen orientation of the repaired tissue at 16 weeks postoperatively, a supplemental evaluation using a polarized light microscope (PLM) (ECLIPSE E600 POL; Nikon, Tokyo, Japan) was conducted (34). This evaluation was performed on HE-stained sections from each group. Two cross polarizers were used so that highly ordered collagen perpendicular to the articular surface appeared bright, while collagen that was not ordered (nonbirefringent) appeared dark. The contrast of fibrils more parallel to the articular surface was darker than collagen oriented perpendicular to the articular surface. To observe the predominant direction of the birefringent regions and confirm the lack of orientation in the nonbirefringent regions, the sections were rotated at 0°, 45°, and 90° for the fixed filters. Microscopic images were acquired using a digital camera (DS-5M-L1, Nikon, Tokyo, Japan). Each sample was examined independently by an experienced PLM user.

Ex vivo analysis of deletion of high-mannose type N-glycan in cartilage

Organ culture experiments in mice were established to study the effects of mannosidase on articular cartilage without immunoreaction and in anticipation of later candidate gene research using transgenic mice. According to the established ethical guidelines approved by the local animal care committee, cartilage catabolism was analyzed by culturing femoral head cartilage of 4-week-old C57BL6 male mice with α-mannosidase (1.9 U/mL) ex vivo (35, 36). Mannosidase was removed on day 3, and organ culture was continued until day 6. To evaluate cartilage degradation, quantification of PG release from cartilage explants was performed using the dimethylmethylene blue assay (36, 37) and exposure to sialidase (1.9 U/mL) and interleukin-1 beta (Cat #. 300-01A; BioLegend, San Diego, CA, USA) (10 ng/mL) was also used as another control. The NO concentration in the culture medium was measured using the Griess reagent system (Promega, Tokyo, Japan). To determine the direct effects of mannosidase on the matrix, some cartilage explants were subjected to freeze-thaw cycles in liquid nitrogen to destroy chondrocytes present in the superficial layer of the cartilage (22, 38). After the procedure, the cells were replaced with the same culture medium described above. Each tissue sample was stained with Safranin O. Lectin staining with Con A (Wako Pure Chemical Industries, Richmond, VA, USA) and PhoSL (J-Oil Mills Inc., Tokyo, Japan) was used to detect the high-mannose type N-glycans. Staining was performed using the ABC Kit (Vector Labs, Burlingame, CA, USA), and the sections were counterstained with HE.

RNA extraction and quantitative RT-PCR analysis

Total RNA was extracted from the samples using an RNeasy Mini Kit (Qiagen, Hilden, Germany). For complementary DNA synthesis, 1.0 μg of RNA was reverse transcribed using random hexamer primers (Promega, Tokyo, Japan) and ImProm II reverse transcriptase (Promega). Quantitative RT-PCR was performed using a Thermal Cycler Dice Real Time System II (Takara Bio Inc., Otsu, Japan) and SYBR Premix Ex Taq II (Takara, Shiga, Japan) with gene-specific primers (S4 Table) in 15 μl of the mixture, following the manufacturer’s instructions. Quantitative data were normalized using peptidylprolyl isomerase A as an endogenous reference gene and were calculated using the ΔΔCt method (39).

Generation of Fut8loxp/loxpCol2a1-Cre cKO mice

Fut8loxp/loxp mice were provided by Tohoku Pharmaceutical University (Sendai, Japan). To interrupt the synthesis of corefucosylated N-glycans in cartilage, we generated mice with knockout of the chondrocyte-specific Fut8 gene (Col2-Fut8-/- mice) by crossing Fut8loxp/loxmice with Col2a1-Cre–transgenic mice (40), in which Cre recombinase is expressed specifically in chondrocytes under the Col2a1 promoter. Transgenic mice carrying the Col2a1-Cre transgene (strain B6; SJL-Tg [Col2a1-Cre] 1Bhr/J; stock number 003554) were obtained from the Jackson Laboratory (Bar Harbor, ME, USA). Homozygous Fut8loxp/loxpmice were bred with Col2a1-Cre mice, and offspring with the genotype Fut8loxp/+ Col2a1-Cre were bred with Fut8loxp/loxp mice to obtain the Fut8loxp/loxpCol2a1-Cre cKO experimental group and Fut8loxp/loxp (flox) littermate controls. All animals were maintained at Hokkaido University under the regulations of the Institutional Animal Care and Use Committee.

Skeletal examination

To observe the skeletal systems, whole skeletons of WT and cKO littermates were stained with alcian blue and alizarin red, as previously described (41, 42). The newborns were skinned, eviscerated, and fixed in 95% ethanol. Intact skeletons were stained with 150 mg/ml of alcian blue 8GX in 75% (vol/vol) ethanol/20% acetic acid for 24–48 hours and excess tissues were removed by 1–2% KOH digestion for 2–3 days. The skeletal preparations were stained with 75 mg/ml of alizarin red S in 1% KOH for 24 hours and cleared in graded glycerol solutions (43).

Instability-induced OA model

An OA model was created in 10-week-old mice by destabilizing the knee joint as previously described (44). With the mice under general anesthesia, we destabilized the right knee joint by transection of the medial collateral ligament and removing the cranial half of the medial meniscus using a microsurgical technique (DMM). A sham operation was performed on the left knee joint using the same approach, without ligament transection and meniscectomy. For histological assessment, the mice were sacrificed, and the entire knee joint was dissected 8 weeks postoperatively.

Age-associated OA model

At 3, 4, 9, and 15 months of age, the mice were sacrificed, and their entire knee joints were dissected to assess the spontaneous development of OA as a model of age-associated OA (44, 45).

Human Cartilage Preparation

Acquisition and use of patient tissues were approved by the institutional review board (IRB) of Hokkaido University (approval number: 014-0144), and informed consent was obtained in advance. Samples were from patients undergoing total knee arthroplasty for clinically and radiologically diagnosed OA (n=5; age range 61–84 years, mean 72.4; male: female ratio 1:4). Age-matched control articular cartilage was from patients undergoing total hip arthroplasty for femoral neck fracture with no history of joint disease (n=5; age range 45–88 years, mean 61.2 years; male: female ratio 3:2). Each cartilage specimen was evaluated macroscopically by at least two veteran doctors to ensure that it had not suffered damage or degeneration and was treated within 9 hours of harvest in the operating room. Immediately upon receipt, isolated human cartilage was homogenized with a Polytron blender (Kinematica, Luzern, Switzerland), and then cold ethanol was added to separate the protein and lipid fractions.

Total cartilage glycomic analysis

To determine whether the glycosylation detected is conserved across species, we analyzed the total glycome in human cartilage. N-glycans were released directly using cartilage lysates following deglycosylation by overnight treatment with peptide N-glycanase F (PNGase F, 2U) (Roche, Switzerland). The supernatants containing GSLs and fOSs were dried with a centrifugal evaporator. GSL-glycans were isolated by enzymatic digestion using EGCase I (Takara Bio Inc. Japan), whereas fOSs were recovered from an EGCase I-free fraction (46). Cartilage lysate was delipidated and digested by GAG disaccharides (47). Extracted glycoproteins were subjected to BEP for O-glycan analysis. Detailed procedures and materials are provided elsewhere (48). N-glycans, fOSs, GAGs, and GSL-glycans were subjected to glycoblotting (49). Purified N-glycans, fOSs, O-glycans, and GSL-glycan solutions were mixed with 2,5-dihydrobenzoic acid and subjected to Matrix-assisted laser desorption/ionization-time of flight mass spectrometry (MALDI-TOF MS). 2AB-labeled GAG disaccharides were analyzed by HPLC. The glycan compositions were manually determined by conducting database searches (i.e., a compositional search of the UniCarbKB database (http://www.unicarbkb.org/query) for fOSs and N- and O-glycans and of the SphinGOMAP database (http://www.sphingomap.org/) for GSL-glycans). All previously deposited GSL-glycans in the SphinGOMAP database were extracted and compiled as an in-house database to allow searching by the m/z value and/or composition. The absolute quantification was obtained by comparative analyses between the MS signal areas derived from each glycan and the internal standard.

Statistics

All data in this study are presented as the mean ± standard deviation and were repeated at least three times unless otherwise indicated. Data analysis was performed using GraphPad Prism 9 software version 9.4.1 (GraphPad Software, Inc., San Diego, CA, USA), and the Welch t-test/Welch analysis of variance with subsequent use of the Tukey–Kramer multiple comparison tests were used to determine significant differences between the groups. P-values <0.05 were considered significant. JMP Pro version 16.2.0 (SAS Institute, Cary, NC, USA) was used to reveal the relationships between each subject of sub glycomes; we performed principal component analysis (PCA) and hierarchical cluster analysis.

Study approval

Acquisition and use of patient tissues were approved by the institutional review board (IRB) of Hokkaido University (approval number: 014-0144), and informed consent was obtained in advance. All animal studies were performed according to established ethical guidelines approved by the local animal care committee.

Data availability

All data reported in this paper is available from the corresponding author upon request. This paper does not report original code. Any additional information required to reanalyze the data reported in this paper is available from the lead contact upon request.

Supporting information